Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-05-07 paper/tidy-missing-data-paper.Rmd
finish graphics section

```{r airquality-upset, fig.height = 3, fig.width = 4, fig.cap = "The pattern of missingness in the airquality dataset shown in an upset plot. Only Ozone and Solar.R have missing values, and Ozone has the most missing values. There are 2 cases where both Solar.R and Ozone have missing values."}
# 
gg_miss_upset(airquality)

@@

Parallel coordinate plots can visualize missingness beyond two dimensions. They transform variables to the same scale, ranging between 0 and 1. The `oceanbuoys` dataset from \pkg{naniar} is used for this visualisation, containing measurements of ocean buoys to understand and predict El Niño and El Niña. Data was collected in 1993 and 1997, and contains measurements of sea and air temperature, humidity, and east west and north south wind speeds. Figure \@ref(fig:parallel-cord-plot) shows a parallel coordinate plot of the `oceanbuoys`, with missing values imputed to be 10% below the range, and values colored according to where humidity was missing (humidity_NA). This shows humidity is missing at low air and sea temperatures, and humidity is missing in one year, and one location.

>>>>

```{r airquality-upset, fig.height = 2, fig.width = 3, fig.cap = "The pattern of missingness in the airquality dataset shown in an upset plot. Only Ozone and Solar.R have missing values, and Ozone has the most missing values. There are 2 cases where both Solar.R and Ozone have missing values."}
# 
gg_miss_upset(airquality)

@@

Parallel coordinate plots can visualize missingness beyond two dimensions. They transform variables to the same scale, ranging between 0 and 1. The `oceanbuoys` dataset from \pkg{naniar} is used for this visualisation, containing measurements of sea and air temperature, humidity, and east west and north south wind speeds. Data was collected in 1993 and 1997, to understand and predict El Niño and El Niña. Figure \@ref(fig:parallel-cord-plot) is a parallel coordinate plot of `oceanbuoys`, with missing values imputed to be 10% below the range, and values colored according to whether humidity was missing (`humidity_NA`). Figure \@ref(fig:parallel-cord-plot) shows humidity is missing at low air and sea temperatures, and humidity is missing in one year, and one location.
